jax-cosmo: End-to-End Differentiable and GPU Accelerated Cosmology Library

### 2022-02-11 paper.tex
Updates from Overleaf

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{amsmath}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}
\usepackage{aas_macros}
%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}

@@

\section{JAX: Autograd meets XLA}

\section{Architecture}

\section{Validation against the Core Cosmology Library (CCL)}

\section{Example of applications}

@@

\subsection{Survey Optimization by FoM Maximization}

@@

>>>>

%% The amssymb package provides various useful mathematical symbols
\usepackage{minted}
\usepackage{amssymb}
\usepackage{amsmath}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}
\usepackage{aas_macros}
%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}

@@

% \section{JAX: Autograd meets XLA}

\section{Architecture}
% Explain how the code is structured, mention some tricks of autodiff if we have some
% Follows a bit the structure of the CCL library

\subsection{Validation against the Core Cosmology Library (CCL)}

\section{Example of applications}
% illustrates why autodiff is interesting from several points of view

\subsection{DES Y1 setting}
% Here we describe the data and 3x2pt model for DES Y1

@@

\begin{minted}{python}
def likelihood(cosmo):
  # Compute mean and covariance of angular Cls, 
  # for specific probes
  mu, cov = gaussian_cl_covariance_and_mean(cosmo, 
                    ell, probes)
  # Return likelihood value
  return gaussian_log_likelihood(data, mu, cov)

# Compute derivatives of the likelihood with 
# respect to cosmological parameters
g = jax.grad(likelihood)(cosmo)

# Compute Fisher matrix of cosmological 
# parameters
F = - jax.hessian(likelihood)(cosmo)
\end{minted}

% Plot showing error in Jacobian computation by finite diff

% Plot showing error on some parameters

\subsection{Survey Optimization by FoM Maximization}
% Needs to mention the tomo challenge, mention that we can backpropagate through a NN and the cosmology model
% Maybe this can be only mentioned in the discussion.

@@

% Here we can implement MOPED for the compression of

\section{Gradient-based fast cosmological inference}

\subsection{Variationnal Inference}

\subsection{Hamiltonian Monte Carlo}

\subsubsection{Introduction}

% Show Joe's vanilla HMC results against Cobaya

\subsubsection{NUTS}

% Show the advantage of using NUTS 
% look at difference in efficiency in terms of how many times we need to call the model.

\subsubsection{Neural Reparametrisation}

\subsection{Discussion}

\section{Conclusion}
